%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ---------- HEADING ----------
\begin{center}
\textbf{\Huge \scshape Muhammad Zamin} \\ \vspace{1pt}
\small
647-764-5530 $|$
\href{mailto:zaminjamal.zj@gmail.com}{zaminjamal.zj@gmail.com} $|$
\href{https://www.linkedin.com/in/mzamin/}{\underline{LinkedIn}} $|$
\href{https://github.com/mz-pixel}{\underline{GitHub}} $|$
\href{https://mzamin.ca}{\underline{Portfolio}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{York University}{Toronto, ON}
{Specialized Honours B.Sc. in Computer Science}{} \newline
\vspace{-5pt}
\item[]
{\small \textbf{Relevant Coursework:} Data Structures \& Algorithms, Software Design, Machine Learning, Computer Security, Big Data, Data Mining, User Interface Design, Mobile Development}

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in,label={}]
\small{\item{

\textbf{Languages:} JavaScript, TypeScript, Java, Python, SQL, C, Bash \

\textbf{Frontend:} React.js, Next.js, Vite, Tailwind CSS, Redux, HTML, shadcn/ui \

\textbf{Backend:} Node.js, Express.js, Spring Boot, REST APIs, WebSockets (Socket.IO), Flask \

\textbf{Databases \& Auth:} PostgreSQL, Supabase, SQLite, JWT, OAuth, MongoDB \

\textbf{Tools \& DevOps:} Docker, Git, Postman, Unix/Linux, CI/CD, NPM, Spark, Hadoop

}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Front-End Developer}{Sep 2025 -- Present}
{Department of Computer Science, Lassonde School of Engineering, York University}{Toronto, ON}

\resumeItemListStart
\resumeItem{Developed a real-time virtual queue system for efficient handling of student service requests.}
\resumeItem{Built a responsive frontend using React.js and Vite with modular components.}
\resumeItem{Applied SDLC principles, translating wireframes into structured implementations.}
\resumeItem{Implemented authentication, session management, and WebSockets for real-time updates.}
\resumeItemListEnd

\resumeSubheading
{Full-Stack Developer}{Jan 2026 -- Mar 2026}
{TMA Student Club, York University}{Toronto, ON}

\resumeItemListStart
\resumeItem{Built a full-stack banquet RSVP platform with user registration and admin check-in mechanisms.}
\resumeItem{Developed frontend with Next.js, React, TypeScript, and Framer Motion for smooth UX.}
\resumeItem{Engineered scalable database architectures with Supabase and secure authentication using Clerk.}
\resumeItem{Implemented secure ticket purchasing and automatic email confirmations using Stripe and Resend.}
\resumeItem{Built an admin dashboard with integrated QR code scanning for seamless event-entry tracking.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Image Classification via CNNs} $|$ \emph{PyTorch, Torchvision, NumPy, Matplotlib}}{}

\resumeItemListStart
\resumeItem{Developed a CNN for multi-class classification on the CIFAR-10 dataset.}
\resumeItem{Achieved 82\% testing accuracy through architecture optimization and hyperparameter tuning.}
\resumeItem{Applied advanced augmentation and normalization using torchvision to improve performance.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Custom Malware Detection using YARA} $|$ \emph{YARA, Linux, Reverse Engineering Tools}}{}

\resumeItemListStart
\resumeItem{Analyzed a Windows malware sample using static analysis to identify suspicious behaviors.}
\resumeItem{Designed a custom YARA rule leveraging PE structure, anomalous timestamps, and string patterns.}
\resumeItem{Engineered multi-condition detection logic and validated accuracy using binwalk and rabin2.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{B-Minor Compiler} $|$ \emph{C, Flex, Bison}}{}

\resumeItemListStart
\resumeItem{Built a C-like language compiler using Flex and Bison for lexical and syntax analysis.}
\resumeItem{Implemented name resolution and semantic type checking to ensure logic and type safety.}
\resumeItem{Built an x86-64 code generator with stack management, control flow handling, and function calls.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
